\documentclass[12pt]{article}

\usepackage{geometry}
\geometry{margin=5em}
\usepackage[export]{adjustbox}
\usepackage{array}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{fancyhdr}
\pagestyle{empty}
\usepackage{lastpage}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{pifont}
\usepackage{graphicx}
\graphicspath{{../img}}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\usepackage{tabularx}
\usepackage{tikz}
\usetikzlibrary{patterns}

\newcommand{\R}{\mathbb R}
\newcommand{\e}{{\rm e}}
\newcommand{\pobr}[1]{\left\langle#1\right\rangle}
\newcommand{\norm}[1]{\lVert #1 \rVert}
\newcommand{\abs}[1]{\lvert #1 \rvert}

\DeclareMathOperator{\xd}{d\!}
\DeclareMathOperator{\proj}{proj}

\title{}
\date{}

\begin{document}
\noindent{\bf\large Name:}

\begin{enumerate}
\item
Write a paragraph of at least {\bf 100 words} describing the difficulties you are currently facing in this math class. 
\vspace{\stretch{1}}

\item Write a paragraph of at least {\bf 100 words} explaining what you typically do when you do not understand a math concept.
\vspace{\stretch{1}}
\clearpage

\item Check the reason(s) why you have “checked out’’ in the math class.
\begin{enumerate}[label = \scalebox{1.5}{$\square$}]
\item
I felt totally lost at times.
\vspace{1em}

\item
The content is too easy and/or repetitive for me.
\vspace{1em}

\item
I think math feels pointless or boring. I don't see its connection to real life.
\vspace{1em}

\item
I don't care about school at the moment.
\vspace{1em}

\item
The classroom environment is very distracting.
\vspace{1em}

\item
I have many life or academic issues to worry about.
\vspace{1em}

\item
I do not get along with the teacher personally.
\vspace{1em}

\item
I do not feel confident in my math skills.
\vspace{1em}


\item
I am overwhelmed by responsibilities outside of school.
\vspace{1em}

\item
Others: \rule{0.7\textwidth}{0.1pt}
\end{enumerate}
\end{enumerate}


\end{document}