\documentclass[12pt]{article}

\usepackage{geometry}
\geometry{margin=5em}
\usepackage[export]{adjustbox}
\usepackage{array}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{fancyhdr}
\pagestyle{empty}
\usepackage{lastpage}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{pifont}
\usepackage{graphicx}
\graphicspath{{../img}}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\usepackage{tabularx}
\usepackage{tikz}
\usetikzlibrary{patterns}

\newcommand{\R}{\mathbb R}
\newcommand{\e}{{\rm e}}
\newcommand{\pobr}[1]{\left\langle#1\right\rangle}
\newcommand{\norm}[1]{\lVert #1 \rVert}
\newcommand{\abs}[1]{\lvert #1 \rvert}

\DeclareMathOperator{\xd}{d\!}
\DeclareMathOperator{\proj}{proj}

\title{}
\date{}

\begin{document}
\begin{center}
\Huge
Teacher's Commitment
\end{center}

The teacher commits to uphold and enforce the classroom norms below in order to maintain a safe, respectful, and productive learning environment.

\section*{Immediate Response} 
\begin{itemize}
\item
\textbf{Strict One Mic Policy.}  
During discussions, only one person speaks at a time.  
First violation: verbal warning.  
Repeated violation: student steps out into the hallway for at least five minutes and a call home will be made.

\item
\textbf{No Head Down.}  
Students must remain attentive and engaged during class.  
First violation: verbal warning.  
Repeated violation: student steps into the hallway for at least one minute or a call home will be made.  
Consecutive violations over two days will result in a call home.

\item
\textbf{No Checked-Out Behavior.}  
Students must stay mentally and emotionally present.  
First violation: verbal warning.  
Repeated violation: student will surrender the distracting item(s) for the rest of the period or a call home will be made.  
Consecutive violations over two days will result in a call home.

\item
\textbf{Respect the Seating Arrangement.}  
Every student must remain at their assigned desk and chair. Unauthorized changes to the seating layout are not allowed.  
First violation: verbal warning.  
Repeated violation: student steps into the hallway for the rest of the period.  
Consecutive violations over two days will result in a call home.
\end{itemize}

\section*{Restorative Practice}
We understand that addressing only the symptoms of a problem without understanding its cause does not lead to real improvement. Therefore, following a call home, the teacher will schedule a restorative conversation with the student to better understand their situation and work together toward a lasting resolution.

\section*{Addendum}
Homework—whether online or offline—is mandatory. A substantial amount of missing or incomplete homework will result in a call home.

\end{document}