\documentclass[twoside, 10pt]{article}
\usepackage{geometry}
\geometry{bottom=4em,top=6em, inner=2.2cm, outer=4em,  headheight=\paperheight}
\usepackage[export]{adjustbox}
\usepackage{array}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{fancyhdr}
\usepackage{luacode}
\newcommand{\assessmentType}{Formative}
\pagestyle{fancy}
\fancyhf{}
\lhead{Precalculus - BASE}
\chead{Spring Mass Motion III}
\directlua{pageNum = 1}
\rhead{AO \assessmentType, Page \directlua{tex.print(pageNum); pageNum = pageNum + 1; if pageNum > 2 then pageNum = 1 end}}
\usepackage{lastpage}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{pifont}
\usepackage{graphicx}
\graphicspath{{../img}}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\usepackage{tabularx}
\usepackage{polynom}

\newcommand{\R}{\mathbb R}
\newcommand{\e}{{\rm e}}
\newcommand{\pobr}[1]{\left\langle#1\right\rangle}
\newcommand{\norm}[1]{\lVert #1 \rVert}
\newcommand{\abs}[1]{\lvert #1 \rvert}

\DeclareMathOperator{\xd}{d\!}
\DeclareMathOperator{\proj}{proj}

\title{}
\date{}

\newcommand{\template}{
\directlua{tex.print(utils.genVersion())}
\noindent
{\large
First Name \rule{8em}{.1pt}\hspace{\stretch{1}} Last Name \rule{8em}{.1pt}\hspace{\stretch{1}} Date \rule{1.5em}{.1pt} -- \rule{1.5em}{.1pt} -- \rule{1.5em}{.1pt}\hspace{\stretch{1}} Period \rule{2em}{.1pt}\hspace{\stretch{1}} 
}
\vspace{1em}

\noindent
\renewcommand{\arraystretch}{2}
\begin{tabular}{|l|l|l|}
\hline
\textbf{ARGUE}&\textbf{MODEL}&\textbf{BE PRECISE}\\
\hline
&&\\
\hline
\end{tabular}
\vspace{2em}

Experiment with the spring-mass motion simulation and answer the questions below.

\begin{enumerate}

\item (\textbf{Be Precise}) Hang the 50\,g load on the spring, then release it from any position. The time it takes for the load to return to the release position after one complete cycle of oscillation is called the \emph{period} of the oscillation.

Since measurement error is inevitable, \textbf{a common technique for improving accuracy is to repeat the measurement several times and then take the average.}

\begin{enumerate}

\item Measure the period of the oscillation for one release position.
\vspace{.5em}

First measurement: \rule{6em}{0.4pt} s
\vspace{.5em}

Second measurement: \rule{6em}{0.4pt} s
\vspace{.5em}

Third measurement: \rule{6em}{0.4pt} s

\vspace{.5em}

The average: \rule{6em}{0.4pt} s
\vspace{\stretch{1}}

\item Measure the period of the oscillation for another release position.
\vspace{.5em}

First measurement: \rule{6em}{0.4pt} s
\vspace{.5em}

Second measurement: \rule{6em}{0.4pt} s
\vspace{.5em}

Third measurement: \rule{6em}{0.4pt} s

\vspace{.5em}

The average: \rule{6em}{0.4pt} s
\vspace{\stretch{1}}

\item Measure the period of the oscillation for a third release position.
\vspace{.5em}

First measurement: \rule{6em}{0.4pt} s
\vspace{.5em}

Second measurement: \rule{6em}{0.4pt} s
\vspace{.5em}

Third measurement: \rule{6em}{0.4pt} s

\vspace{.5em}

The average: \rule{6em}{0.4pt} s
\vspace{\stretch{1}}

\end{enumerate}

\item \label{model} (\textbf{Model}) What did you observe from the previous experiment? Write a hypothesis describing the relationship between the period and the release position in spring-mass motion for a fixed load.

From the experiment, we observed that the periods for different release position seem to be \rule{6em}{.4pt}.
\vspace{1em}

Therefore, we hypothesize that the period is \rule{10em}{0.4pt} the release position.
\vspace{\stretch{1}}

\item (\textbf{Argue}) Explain how you would experimentally verify the hypothesis you made in Problem~\ref{model}.
\vspace{1em}

To verify the hypothesis experimentally, we will repeat the experiment with different \rule{6em}{0.4pt} and different \rule{6em}{0.4pt}. 
\vspace{\stretch{1}}

\clearpage

\item (\textbf{Be Precise}) Carry out your verification using the 100\,g and 250\,g loads with the same spring. Find the period for each load. Don't forget to repeat the measurement several times and then take the average.
\vspace{1em}

The period for the 100\,g load is \rule{6em}{0.4pt} s
\vspace{1em}

The period for the 250\,g load is \rule{6em}{0.4pt} s

\vspace{\stretch{1}}

\item (\textbf{Argue}) Is the period proportional to the mass of the load? Explain why or why not.
\vspace{1em}

The period for the 50\,g load is \rule{6em}{0.4pt}, and the mass/period ratio is  \rule{6em}{0.4pt}.
\vspace{1em}

The period for the 100\,g load is \rule{6em}{0.4pt}, and the mass/period ratio is  \rule{6em}{0.4pt}.
\vspace{1em}

Because the ratios are  \rule{6em}{0.4pt}, the period \rule{6em}{0.4pt} proportional to the mass of the load.
\vspace{\stretch{1}}

\item (\textbf{Argue}) Is the period proportional to the square root of the mass of the load? Explain why or why not.
\vspace{1em}

The period for the 50\,g load is \rule{6em}{0.4pt}, the square root of $50$  is \rule{6em}{0.4pt}, and the \textit{( square root of mass)/period} ratio is  \rule{6em}{0.4pt}.
\vspace{1em}

The period for the 100\,g load is \rule{6em}{0.4pt},  the square root of $100$  is \rule{6em}{0.4pt}, and the \textit{( square root of mass)/period} ratio is  \rule{6em}{0.4pt}.
\vspace{1em}

Because the ratios are  \rule{6em}{0.4pt}, the period \rule{6em}{0.4pt} proportional to the square root of the mass of the load.
\vspace{\stretch{1}}

\item (\textbf{Model}) Explain how the period can be used to determine the unknown mass of a load.
\vspace{1em}

Let $p$ be the period, and $m$ be the mass.
\vspace{1em}

From the experiment data, we found that $k = \frac{\sqrt m}{p} = \rule{6em}{0.4pt}$. 
\vspace{1em}

Consequently,  $\sqrt m = \rule{6em}{0.4pt}$, and $m = \rule{6em}{0.4pt}$. 

\vspace{\stretch{1}}

\item (\textbf{Be Precise}) Use the period to determine the mass of the purple (small) load. Show all your work.
\vspace{1em}

The period for the purple load is \rule{6em}{0.4pt}. Therefore, from the formula above, the mass of the purple load is 
\vspace{1em}

\[
\rule{12em}{0.4pt} = \rule{6em}{0.4pt}
\]

\vspace{\stretch{1}}

\end{enumerate}
}
\begin{luacode*}
utils = require("../utils")
\end{luacode*}

\begin{document}
\begin{luacode}
for i=1,1 do
	if i == 2 then
		tex.print("\\renewcommand{\\assessmentType}{Summative}")
	end
	tex.print("\\template")	
end
\end{luacode}
\end{document}