\documentclass[twoside, 10pt]{article}
\usepackage{geometry}
\geometry{bottom=4em,top=6em, inner=2.2cm, outer=4em,  headheight=\paperheight}
\usepackage[export]{adjustbox}
\usepackage{array}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{fancyhdr}
\usepackage{luacode}
\newcommand{\assessmentType}{Formative}
\pagestyle{fancy}
\fancyhf{}
\lhead{Precalculus - BASE}
\chead{Spring Mass Motion II}
\directlua{pageNum = 1}
\rhead{AO \assessmentType, Page \directlua{tex.print(pageNum); pageNum = pageNum + 1; if pageNum > 2 then pageNum = 1 end}}
\usepackage{lastpage}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{pifont}
\usepackage{graphicx}
\graphicspath{{../img}}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\usepackage{tabularx}
\usepackage{polynom}
\usepackage{setspace}

\newcommand{\R}{\mathbb R}
\newcommand{\e}{{\rm e}}
\newcommand{\pobr}[1]{\left\langle#1\right\rangle}
\newcommand{\norm}[1]{\lVert #1 \rVert}
\newcommand{\abs}[1]{\lvert #1 \rvert}


\DeclareMathOperator{\xd}{d\!}
\DeclareMathOperator{\proj}{proj}

\title{}
\date{}

\newcommand{\template}{
\newcommand{\blankfillspacing}{2.5}
\directlua{tex.print(utils.genVersion())}
\noindent
{\large
First Name \rule{8em}{.1pt}\hspace{\stretch{1}} Last Name \rule{8em}{.1pt}\hspace{\stretch{1}} Date \rule{1.5em}{.1pt} -- \rule{1.5em}{.1pt} -- \rule{1.5em}{.1pt}\hspace{\stretch{1}} Period \rule{2em}{.1pt}\hspace{\stretch{1}} 
}
\vspace{1em}

\noindent
\renewcommand{\arraystretch}{2}
\begin{tabular}{|l|l|l|}
\hline
\textbf{ARGUE}&\textbf{MODEL}&\textbf{BE PRECISE}\\
\hline
&&\\
\hline
\end{tabular}
\vspace{2em}

Experiment with the Spring Mass Motion Simulation, and answer the questions below.

\begin{enumerate}

\item\label{letgo} (\textbf{Be Precise}) Measure the distance between the equilibrium position and each of the following:
\begin{enumerate}
\item
the position where you release the load. \rule{5em}{0.4pt}\\[2em]

\item 
the highest position reached by the load. \rule{5em}{0.4pt}\\[2em]

\item
the lowest position reached by the load. \rule{5em}{0.4pt}
\end{enumerate}

\item\label{theory} (\textbf{Model}) Perform the experiment in Problem \ref{letgo} using a few different release positions. List all your results, then make a hypothesis about the relationship among the three quantities.

\begin{itemize}

\item
Experiment Results:

\begin{center}
\renewcommand{\arraystretch}{4}
\newcommand{\cellwidth}{15em}
\begin{tabular}{|c|c|c|}
\hline
&Release Position 1&Release Position 2\\
\hline
Release Position&\, \hspace{\cellwidth}\, &\, \hspace{\cellwidth}\, \\
\hline
Highest Position&&\\
\hline
Lowest Position&&\\
\hline
\end{tabular}
\end{center}

\vspace{\stretch{2}}

\item 
Hypothesis:

\vspace{1em}

\begin{spacing}{\blankfillspacing}
The distances from the equilibrium position to the release position, the highest position, and the lowest position are \rule{10em}{0.4pt} regardless of the release position.
\end{spacing}

\vspace{\stretch{1}}

\end{itemize}

\clearpage

\vspace{\stretch{1}}

\item (\textbf{Argue}) Based on the theory you came up with in Problem \ref{theory}, what will happen if you release the load exactly at the equilibrium position? Explain your reasoning.

\vspace{1em}

\begin{spacing}{\blankfillspacing}
When you release the load exactly at the equilibrium position, the distance from the equilibrium position to the release point is \rule{6em}{0.4pt}. Therefore, the distances from the equilibrium position to the highest and lowest positions are also \rule{6em}{0.4pt}. Hence, the spring is \rule{10em}{0.4pt}.
\end{spacing}

\vspace{\stretch{1}}

\item(\textbf{Model}) In reality, the equilibrium position will not magically appear by clicking a button. However, the highest and lowest positions can still be observed. \textbf{Design a method, based on the theory you came up with in Problem \ref{theory}, to determine the equilibrium position of a load.}

\vspace{1em}

\begin{spacing}{\blankfillspacing}
Because the distances from the highest and lowest positions to the equilibrium position are \rule{10em}{0.4pt}, the equilibrium position is located \rule{10em}{0.4pt} between the highest and lowest positions.
\end{spacing}

\vspace{\stretch{1}}

\item(\textbf{Argue}) Use the approach you designed to find the distance between the natural length and the equilibrium position of the purple (small) load. Show all your experimental results and calculations.

\vspace{1em}

\begin{spacing}{\blankfillspacing}
Align the 50 mm mark of the ruler with the natural length. My highest point was at the \rule{6em}{0.4pt} mark, and my lowest point was at the \rule{6em}{0.4pt} mark. Therefore, the equilibrium position must be at the \rule{6em}{0.4pt} mark. Hence, the distance between the natural length and the equilibrium position is \rule{10em}{0.4pt}.
\end{spacing}

\vspace{\stretch{1}}

\end{enumerate}
}

\begin{luacode*}
utils = require("../utils")
\end{luacode*}

\begin{document}
\begin{luacode}
for i=1,1 do
	if i == 2 then
		tex.print("\\renewcommand{\\assessmentType}{Summative}")
	end
	tex.print("\\template")	
end
\end{luacode}

\end{document}