\documentclass[twoside, 10pt]{article}
\usepackage{geometry}
\geometry{bottom=4em,top=6em, inner=2.2cm, outer=4em,  headheight=\paperheight}
\usepackage[export]{adjustbox}
\usepackage{array}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{fancyhdr}
\usepackage{luacode}
\newcommand{\assessmentType}{Formative}
\pagestyle{fancy}
\fancyhf{}
\lhead{Precalculus - BASE}
\chead{Spring Mass Motion I}
\directlua{pageNum = 1}
\rhead{AO \assessmentType, Page \directlua{tex.print(pageNum); pageNum = pageNum + 1; if pageNum > 2 then pageNum = 1 end}}
\usepackage{lastpage}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{pifont}
\usepackage{graphicx}
\graphicspath{{../img}}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\usepackage{tabularx}
\usepackage{polynom}

\newcommand{\R}{\mathbb R}
\newcommand{\e}{{\rm e}}
\newcommand{\pobr}[1]{\left\langle#1\right\rangle}
\newcommand{\norm}[1]{\lVert #1 \rVert}
\newcommand{\abs}[1]{\lvert #1 \rvert}

\DeclareMathOperator{\xd}{d\!}
\DeclareMathOperator{\proj}{proj}

\title{}
\date{}

\newcommand{\template}{
\directlua{tex.print(utils.genVersion())}
\noindent
{\large
First Name \rule{6em}{.1pt}\hspace{\stretch{1}} Last Name \rule{6em}{.1pt}\hspace{\stretch{1}} Date \rule{1.5em}{.1pt} -- \rule{1.5em}{.1pt} -- \rule{1.5em}{.1pt}\hspace{\stretch{1}} Period \rule{2em}{.1pt}\hspace{\stretch{1}} Score \rule{2em}{.1pt}
}
\vspace{1em}

\noindent
\renewcommand{\arraystretch}{2}
\begin{tabular}{|l|l|l|}
\hline
\textbf{ARGUE}&\textbf{MODEL}&\textbf{BE PRECISE}\\
\hline
&&\\
\hline
\end{tabular}
\vspace{2em}

Experiment with the Spring Mass Motion Simulation, and answer the questions below.
\begin{enumerate}

\item (\textbf{Be Precise}) Measure the distance between the natural position of the spring and the equilibrium position of the spring when the load is
\begin{enumerate}
\item
50g \rule{5em}{0.4pt}\\[2em]
\item 
100g \rule{5em}{0.4pt}
\end{enumerate}

\item\label{proportion} (\textbf{Model}) Describe a quantitative relationship between the load ($m$) and the displacement of the equilibrium from the natural position ($d$). Is the relationship proportional? If so, propose a model of the form $d=k\cdot m$ and estimate k.
\vspace{\stretch{1}}
\item\label{letgo} (\textbf{Be Precise}) Measure the distance between the equilibrium position and
\begin{enumerate}
\item
the place you let go of the load. \rule{5em}{0.4pt}\\[2em]
\item 
the highest position of the load. \rule{5em}{0.4pt}\\[2em]
\item
the lowest position of the load. \rule{5em}{0.4pt}
\end{enumerate}
\item\label{theory} (\textbf{Model}) Do the experiment in Problem \ref{letgo} a few times for different let-go positions, then theorize your observation.
\vspace{\stretch{1}}
\item (\textbf{Argue}) Based on the theory you come up with in Problem \ref{theory}, what will happen if you let go of the load right at the equilibrium position? Explain your reasoning.
\vspace{\stretch{1}}
\clearpage
\item (\textbf{Argue}) If you made an estimate of $k$ in Problem \ref{proportion}, explain how you will experimentally verify your estimate. You may use any loads with known mass.
\vspace{\stretch{1}}
\item(\textbf{Be Precise}) Carry out your verification with the 100g and 250g load. Show your calculation.
\vspace{\stretch{1}}
\item(\textbf{Model}) Use the model you found above to estimate the mass of the purple(small), blue(medium) and orange(large) load. Show all your work.
\vspace{\stretch{1}}
\end{enumerate}
}

\begin{luacode*}
utils = require("../utils")
\end{luacode*}

\begin{document}
\begin{luacode}
for i=1,1 do
	if i == 2 then
		tex.print("\\renewcommand{\\assessmentType}{Summative}")
	end
	tex.print("\\template")	
end
\end{luacode}
\end{document}