\documentclass[twoside, 10pt]{article}
\usepackage{geometry}
\geometry{bottom=4em,top=6em, inner=2.2cm, outer=4em,  headheight=\paperheight}
\usepackage[export]{adjustbox}
\usepackage{array}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{fancyhdr}
\usepackage{luacode}
\pagestyle{fancy}
\fancyhf{}
\lhead{Precalculus - BASE}
\chead{Logarithms I}
\directlua{pageNum = 1}
\rhead{AO Test, Page \directlua{tex.print(pageNum); pageNum = pageNum + 1; if pageNum > 3 then pageNum = 1 end}}
\usepackage{lastpage}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{pifont}
\usepackage{graphicx}
\graphicspath{{../img}}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\usepackage{tabularx}
\usepackage{polynom}

\newcommand{\R}{\mathbb R}
\newcommand{\e}{{\rm e}}
\newcommand{\pobr}[1]{\left\langle#1\right\rangle}
\newcommand{\norm}[1]{\lVert #1 \rVert}
\newcommand{\abs}[1]{\lvert #1 \rvert}

\DeclareMathOperator{\xd}{d\!}
\DeclareMathOperator{\proj}{proj}

\title{}
\date{}

\newcommand{\template}{
\directlua{tex.print(utils.genVersion())}
\noindent
{\large
First Name \rule{6em}{.1pt}\hspace{\stretch{1}} Last Name \rule{6em}{.1pt}\hspace{\stretch{1}} Date \rule{1.5em}{.1pt} -- \rule{1.5em}{.1pt} -- \rule{1.5em}{.1pt}\hspace{\stretch{1}} Period \rule{2em}{.1pt}\hspace{\stretch{1}} Score \rule{2em}{.1pt}
}
\vspace{1em}
\begin{enumerate}
\item ({\textbf{Be Precise}}) Score: \rule{2em}{.4pt} 
\begin{enumerate}
\item
Find the value of the following expressions
\begin{enumerate}
\item
\directlua{b = utils.genRandom(2,5, false, false, false); e = utils.genRandom(-3, 3, false, false,false)}
$\log_\directlua{tex.print(b)}\left(\directlua{tex.print(utils.printFraction(b,e))}\right)$
\vspace{\stretch{1}}
\item
\directlua{b = utils.genRandom(2,9, false, false, false); e = utils.genRandom(-5, 5, false, false,false); c = utils.genRandom(2,9, false, false, false)}
$\directlua{tex.print(b)}^{\log_\directlua{tex.print(b)}\left(\directlua{tex.print(utils.printFraction(c,e))}\right)}$
\vspace{\stretch{1}}
\end{enumerate}
\item
In our information-rich era, knowledge is no longer scarce. The more valuable skill is knowing how to verify information. For instance, if you ask ChatGPT, “What is a solution to an equation?”, it will generate the following response.

A \textbf{solution to an equation} is a value (or set of values) that makes the equation \textbf{true} when substituted into it.

An equation states that two expressions are equal.  
A solution is the number (or numbers) that make both sides equal.

\subsection*{Example 1}

\[
x + 3 = 7
\]

Substitute \( x = 4 \):

\[
4 + 3 = 7
\]

Since this statement is true, \( 4 \) is a solution.

\subsection*{Example 2}

\[
x^2 = 9
\]

Two numbers satisfy this equation:

\[
3^2 = 9
\]

\[
(-3)^2 = 9
\]

So the solutions are \( x = 3 \) and \( x = -3 \).

\subsection*{Key Idea}

A solution must make the equation true when substituted in.  
Not every number is a solution --- only those that make the statement correct.

\textbf{Here is the question for you:}
\begin{enumerate}
\item
Is $x = 2$ a solution of $(x-3)(x+2) - 8 = -8$? Explain.
\vspace{\stretch{1}}
\item Find all solutions of  $(x-3)(x+2) - 8 = -8$.
\vspace{\stretch{1}}
\end{enumerate}
\clearpage
\end{enumerate}
\item ({\textbf{Argue}}) Score: \rule{2em}{.4pt} 
\begin{enumerate}
\item
Solve the equation system
\directlua{l = utils.genRandom(-9,9, false, false); m = utils.genRandom(-9,9, false, false, -l)}
\begin{align*}
y &=  \directlua{tex.print(utils.normalizeCoeff(-l - m, false, true))}x\\
y & = x^2\directlua{tex.print(utils.normalizeCoeff(l * m, true, true))}
\end{align*}
\vspace{\stretch{1}}
\item 
\directlua{l = utils.genRandom(-9,9, false, false); m = utils.genRandom(-9,9, false, false, -l)}
Solve the equation for $x$:
\[
(\ln x)^2 \directlua{tex.print(utils.normalizeCoeff(l + m, true, true))}\ln x \directlua{tex.print(utils.normalizeCoeff(l * m, true, true))} = 0
\]
\vspace{\stretch{1}}
\end{enumerate}
\end{enumerate}
\clearpage
}

\begin{luacode*}
utils = require("../utils")
\end{luacode*}

\begin{document}
\begin{luacode}
for i=1,4 do
	tex.print("\\template")
end
\end{luacode}
\end{document}