\documentclass[twoside, 10pt]{article}

\usepackage{geometry}
\geometry{margin=2em,top=6em, inner=2.5cm, headheight=\paperheight}
\usepackage[export]{adjustbox}
\usepackage{array}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\lhead{Precalculus - BASE}
\chead{Average Velocity}
\rhead{Practice, Page \thepage}
\usepackage{lastpage}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{pifont}
\usepackage{graphicx}
\graphicspath{{../img}}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\usepackage{tabularx}
\usepackage{luacode}

\newcommand{\R}{\mathbb R}
\newcommand{\e}{{\rm e}}
\newcommand{\pobr}[1]{\left\langle#1\right\rangle}
\newcommand{\norm}[1]{\lVert #1 \rVert}
\newcommand{\abs}[1]{\lvert #1 \rvert}

\DeclareMathOperator{\xd}{d\!}
\DeclareMathOperator{\proj}{proj}

\title{}
\date{}

\begin{document}
\noindent
{\large
First Name \rule{6em}{.1pt}\hspace{\stretch{1}}Last Name \rule{6em}{.1pt}\hspace{\stretch{1}} Date \rule{1.5em}{.1pt} -- \rule{1.5em}{.1pt} -- \rule{1.5em}{.1pt}\hspace{\stretch{1}} Period \rule{2em}{.1pt}\hspace{\stretch{1}} Score \rule{2em}{.1pt}
}
\vspace{1em}

{\noindent\bf Targets.}
\begin{itemize}
    \item to calculate the average velocity over a time interval, given the position
    \item to numerically determine the limit of the average velocity as the time interval getting shorter
\end{itemize}
{\noindent\bf Do Now.}

Is the free falling motion of uniform velocity? How can you experimentally verify your claim?
{\noindent\bf Concepts.}
\begin{itemize}
\item
Average Velocity
\vspace{\stretch{1}}
\end{itemize}

{\noindent\bf Problems.}

Let $t$ be the time, and $p(t) = -16t^2 + 100$ be the position of an object dropped from 100 feet above the ground. Calculate the average velocity over the time interval $[2, 2+\Delta t]$ for various $\Delta t$. Complete the table below.
\vspace{1em}

\begin{luacode*}
tex.print("\\begin{center}\\renewcommand{\\arraystretch}{2}")
tex.print("\\begin{tabular}{|c|c|}")
tex.print("\\hline\\textbf{$\\Delta t$} & \\textbf{$\\bar{v}$} \\\\ \\hline")
local x = 1
for i = 1,5 do
  x = x /10
  local s = string.format("%.6f", x):gsub("0+$", ""):gsub("%.$", "")
  tex.print(string.format("%s & \\hspace{5em} \\\\ \\hline", s))
end
tex.print("\\end{tabular}")
tex.print("\\end{center}")
\end{luacode*}
\vspace{1em}

{\bf\noindent Discussion.}

Does the average velocity in the table above seem to stably approach a specific number? What number would that be?
\vspace{\stretch{1}}

{\noindent\bf Exit Ticket.} 

Suppose the position of an object over time is given by $p(t) = \sin(t)$.\footnote{This type of motion is frequently seen in real life, too. For example, the oscillatory motion of a ball attached to a spring.} Find the average velocity over the time interval $[0, \pi/2]$.
\vspace{\stretch{1}}

\end{document}