\documentclass[twoside, 10pt]{article}

\usepackage{geometry}
\geometry{bottom=4em,top=6em, inner=2.2cm, outer=4em,  headheight=\paperheight}
\usepackage[export]{adjustbox}
\usepackage{array}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\lhead{Precalculus - BASE}
\chead{The Mystery: $0/0$ }
\rhead{Practice, Page \thepage}
\usepackage{lastpage}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{pifont}
\usepackage{graphicx}
\graphicspath{{../img}}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\usepackage{tabularx}

\newcommand{\R}{\mathbb R}
\newcommand{\e}{{\rm e}}
\newcommand{\pobr}[1]{\left\langle#1\right\rangle}
\newcommand{\norm}[1]{\lVert #1 \rVert}
\newcommand{\abs}[1]{\lvert #1 \rvert}

\DeclareMathOperator{\xd}{d\!}
\DeclareMathOperator{\proj}{proj}

\title{}
\date{}

\begin{document}
\noindent
{\large
First Name \rule{6em}{.1pt}\hspace{\stretch{1}}Last Name \rule{6em}{.1pt}\hspace{\stretch{1}} Date \rule{1.5em}{.1pt} -- \rule{1.5em}{.1pt} -- \rule{1.5em}{.1pt}\hspace{\stretch{1}} Period \rule{2em}{.1pt}\hspace{\stretch{1}} Score \rule{2em}{.1pt}
}
\vspace{1em}

{\noindent\bf Discussion.} What is $\displaystyle \frac{0}{0}$?
\clearpage
\begin{center}
{\it What if schools are all about credentialing and examination?}
\end{center}
\vspace{5em}

{\noindent\bf Survey.}
\vspace{2em}

First Name \rule{10em}{.1pt}\hspace{2em}Last Name \rule{10em}{.1pt}
\begin{enumerate}
\item Please check the box of the Regents Exam you've passed.

\scalebox{1.5}{$\square$} Algebra I\hspace{\stretch{1}}\scalebox{1.5}{$\square$} Geometry\hspace{\stretch{1}}\scalebox{1.5}{$\square$} Algebra II

\item Are you willing to take an adequate amount of practice/drilling to prepare for the retake of any Regents Exams that you've not passed?
\vspace{2em}

\rule{5em}{.1pt}.
\item Do you plan to take the SAT/ACT exam? When?
\vspace{2em}

\rule{.9\textwidth}{.1pt}.
\item How strong is your willingness to spend personal time in preparing for the AP Calculus Exam?

$\bigcirc$ Very Strong\hspace{\stretch{1}}$\bigcirc$ Strong\hspace{\stretch{1}}$\bigcirc$ Neutral\hspace{\stretch{1}}$\bigcirc$ Not Strong \hspace{\stretch{1}}$\bigcirc$ Not At All
\item How to you rank the importance to you among the Regents Exams, the SAT/ACT Exams, and the AP 
Calculus Exams?
\vspace{2em}

\rule{.9\textwidth}{.1pt}.
\end{enumerate}

\end{document}