\documentclass[twoside, 10pt]{article}

\usepackage{geometry}
\geometry{outer=3em, inner=2.2cm, top=6em, bottom=4em, headheight=\paperheight}
\usepackage[export]{adjustbox}
\usepackage{array}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\lhead{Algebra II - BASE}
\chead{Exponential Functions}
\rhead{AO Test, Page \thepage}
\usepackage{lastpage}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{pifont}
\usepackage{graphicx}
\graphicspath{{../img}}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\usepackage{tabularx}
\usepackage{tikz}
\usetikzlibrary{patterns}
\usepackage{luacode}

\newcommand{\R}{\mathbb R}
\newcommand{\e}{{\rm e}}
\newcommand{\pobr}[1]{\left\langle#1\right\rangle}
\newcommand{\norm}[1]{\lVert #1 \rVert}
\newcommand{\abs}[1]{\lvert #1 \rvert}

\DeclareMathOperator{\xd}{d\!}
\DeclareMathOperator{\proj}{proj}

\title{}
\date{}

\begin{document}
\noindent
{\large
First Name \rule{6em}{.1pt}\hspace{\stretch{1}}Last Name \rule{6em}{.1pt}\hspace{\stretch{1}} Date \rule{1.5em}{.1pt} -- \rule{1.5em}{.1pt} -- \rule{1.5em}{.1pt}\hspace{\stretch{1}} Period \rule{2em}{.1pt}\hspace{\stretch{1}} Score \rule{2em}{.1pt}
}
\vspace{1em}

\begingroup
\renewcommand{\arraystretch}{1.5}
\begin{center}
\tiny
{
\begin{tabularx}{\textwidth}{|X|X|X|X|X|X|}
\hline
\bf BE PRECISE & \centerline{Integrating} & \centerline{Applying} & \centerline{Practicing} & \centerline{Acquiring} & \centerline{Awaiting Evidence} \\
\hline
I can calculate accurately and efficiently, and be precise in all of my math.&
Selects and applies the correct procedure and solves all routine AND integrating problems.

AND

Expresses the answer to the correct level of precision needed for the problem (including the correct rounding, units, math symbols, labeling, graphing, vocab…)
&Selects and applies the correct procedure and solves all routine problems.


AND

Expresses the answer to the correct level of precision needed for the problem (including the correct rounding, units, math symbols, labeling, graphing, vocab…)
&Selects and applies the correct procedure and solves most routine problems.


AND

Expresses the answer to the correct level of precision needed for the problem (including the correct rounding, units, math symbols, labeling, graphing, vocab…)
&Selects and applies the correct procedure and solves some routine problems.


AND

Attempts to express the answer to the correct level of precision needed for the problem (including the correct rounding, units, math symbols, labeling, graphing, vocab…).
&Selects and attempts to apply the correct procedure for some routine problems.\\
\hline
\bf Criteria&\multicolumn{5}{l|}{\parbox[c][4em]{.8\textwidth}{}}\\
\hline
\end{tabularx}
}
\end{center}
\endgroup

\begin{luacode*}
math.randomseed(os.time())
car_price = 20000 + 500*math.random(0, 40)
depreciate_rate = math.random(80,90)/100
car_value = string.format("$f(t) = %d(%.2f)^t$", car_price, depreciate_rate)
car_year = math.random(3,8)
after_price = string.format("%.0f", car_price*.5)
home_price=600000 + 5000 * math.random(0, 60)
home_year=math.random(30,70)
appreciate_rate = math.random(2,5)
\end{luacode*}

\begin{enumerate}[leftmargin=*]
\item
The equation \directlua{tex.print(car_value)} represents the value of a car, in dollars, $t$ years after it was purchased.
\begin{enumerate}
\item
What was the purchasing price of the car?
\item 
What is the rate at which the car depreciates every year?
\item
How much is the car worth after \directlua{tex.print(car_year)} years?
\item 
Will the value of the car be more than \$\directlua{tex.print(after_price)} ten years after it was purchased? Show your calculation.
\end{enumerate}

\item A home is purchased for \$\directlua{tex.print(home_price)}. Since then, its value has increased \directlua{tex.print(appreciate_rate)}\% per year.
\begin{enumerate}
\item
Write an equation, in function notation, to represent the value of the home as a function of time in years since it was purchased, $t$.

\item What is the value of the home \directlua{tex.print(home_year)} years after it was purchased (assuming that the trend continues)? Show your calculation.
\end{enumerate}
\item the graph shows a rabbit population that has been growing exponentially.

\begin{tikzpicture}
\begin{axis}[
axis lines=middle,
ylabel={$r$},
xlabel={$t$},
grid=both,
ymin=0,
ytick distance = 15,
xtick distance = 1,
width = 0.55\textwidth
]
\addplot[thick, domain=0:4]{60*(1.5^x)};
\end{axis}
\end{tikzpicture}
\begin{enumerate}
\item
What was the population when it was first measured?
\item By what factor did the population grow in the first year?
\item Write an equation relating the rabbit population, $r$, and the number of years since it was first measured, $t$.
\item What was the population after \textbf{18 months} since it was first measured?
\end{enumerate}

\end{enumerate}
\end{document}