\documentclass[twoside, 10pt]{article}
\usepackage{geometry}
\geometry{bottom=4em,top=6em, inner=2.2cm, outer=4em,  headheight=\paperheight}
\usepackage[export]{adjustbox}
\usepackage{array}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{fancyhdr}
\usepackage{luacode}
\newcommand{\assessmentType}{Formative}
\pagestyle{fancy}
\fancyhf{}
\lhead{Alagebra II - BASE}
\chead{Complex Number Multiplication}
\directlua{pageNum = 1}
\rhead{AO \assessmentType, Page \directlua{tex.print(pageNum); pageNum = pageNum + 1; if pageNum > 3 then pageNum = 1 end}}
\usepackage{lastpage}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{pifont}
\usepackage{graphicx}
\graphicspath{{../img}}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\usepackage{tabularx}
\usepackage{polynom}

\newcommand{\R}{\mathbb R}
\newcommand{\e}{{\rm e}}
\newcommand{\pobr}[1]{\left\langle#1\right\rangle}
\newcommand{\norm}[1]{\lVert #1 \rVert}
\newcommand{\abs}[1]{\lvert #1 \rvert}

\DeclareMathOperator{\xd}{d\!}
\DeclareMathOperator{\proj}{proj}

\title{}
\date{}

\newcommand{\template}{
\directlua{tex.print(utils.genVersion())}
\noindent
{\large
First Name \rule{8em}{.4pt}\hspace{\stretch{1}} Last Name \rule{8em}{.4pt}\hspace{\stretch{1}} Date \rule{1.5em}{.4pt} -- \rule{1.5em}{.4pt} -- \rule{1.5em}{.4pt}\hspace{\stretch{1}} Period \rule{2em}{.4pt}\hspace{\stretch{1}}
}
\vspace{1em}

\noindent
\renewcommand{\arraystretch}{2}
\begin{tabular}{|l|l|l|}
\hline
\textbf{ARGUE}&\textbf{MODEL}&\textbf{BE PRECISE}\\
\hline
&&\\
\hline
\end{tabular}

\vspace{1em}
\noindent
\textbf{Tools:} calculator, ruler, protractor 
\vspace{1em}

\noindent
\textbf{Example}. Let $\displaystyle v = \frac{\sqrt2}{2} + \frac{\sqrt2}{2}i$. The measure of the angle between the positive real axis and the ray from the origin to $v$ is $45^\circ$ and the distance from the origin to $v$ is $1$. See the figure below.

\begin{center}
\begin{tikzpicture}
\begin{axis}[
xlabel={$Re$},
ylabel={$Im$},
axis lines=middle,
ymin=-3.5, ymax=3.5,
xmin=-3.5, xmax=3.5,
yticklabel={$\pgfmathprintnumber{\tick}i$},
width=7in,
height=7in,
grid = both,
xtick distance = 1,
ytick distance = 1,
minor y tick num = 4,
minor x tick num = 4,
grid style={draw=gray!80, dashed}
]
\draw[fill=black] (0.707,0.707) circle (2pt);
\draw[fill=black] (0.707,0.907) node{\Large $v$} ;
\draw[thick] (0,0) -- (0.707,0.707);
\draw[thick] (0,0) -- (1,0);
\draw (0.5, 0.2) node{\large $45^\circ$};
\draw (0.25, 0.4) node{\large $1$};
\end{axis}
\end{tikzpicture}
\end{center}
Here the unit of length is $1$ inch. You are encouraged to remeasure the distance and the angle with the hand tools as practice for using the tools.
\clearpage
\begin{enumerate}
\item (\textbf{Be Precise}) Let $\displaystyle w = \frac{\sqrt 3}{2} + \frac{1}{2}i$. Plot $w$ in the complex plan below, and measure the angle between the positive real axis and the ray from the origin to $w$ and the distance from the origin to $w$. Label the measure of the angle and the distance on the graph.
\begin{center}
\begin{tikzpicture}
\begin{axis}[
xlabel={$Re$},
ylabel={$Im$},
axis lines=middle,
ymin=-3.5, ymax=3.5,
xmin=-3.5, xmax=3.5,
yticklabel={$\pgfmathprintnumber{\tick}i$},
width=7in,
height=7in,
grid = both,
xtick distance = 1,
ytick distance = 1,
minor y tick num = 4,
minor x tick num = 4,
grid style={draw=gray!80, dashed}
]
\end{axis}
\end{tikzpicture}
\end{center}
\item (\textbf{Argue}) Let $z = 1 + 2i$. Calculate $z \cdot w$. Show your work.
\clearpage
\item (\textbf{Be Precise}) Plot $z$ and $z\cdot w$ in the complex plan below, and measure the angle between the ray from the origin to $z$ and the ray from the origin to $z\cdot w$. Label the measure of the angle on the graph.
\begin{center}
\begin{tikzpicture}
\begin{axis}[
xlabel={$Re$},
ylabel={$Im$},
axis lines=middle,
ymin=-3.5, ymax=3.5,
xmin=-3.5, xmax=3.5,
yticklabel={$\pgfmathprintnumber{\tick}i$},
width=7in,
height=7in,
grid = both,
xtick distance = 1,
ytick distance = 1,
minor y tick num = 4,
minor x tick num = 4,
grid style={draw=gray!80, dashed}
]
\end{axis}
\end{tikzpicture}
\end{center}
\vspace{\stretch{1}}
\item\label{hypothesis} (\textbf{Model}) Examining the first graph and second graph, how would you describe what multiplying by $w$ does to $z$?

Hint: Complete the following sentence. Multiplying $z$ by $w$ will rotate $z$ about the origin counterclockwise by\\[1em] \rule{6em}{0.4pt} degrees, which is precisely the measure of the angle between $w$ and the positive $x$-axis.
\clearpage
\item\label{plan}  (\textbf{Model}) You want to test the model you came up with in Problem \ref{hypothesis} with a few more experiments. Let $z_1 = -1 + i$, $z_2= -1 + 0.6i$ and $z_3 = 1 - 1.8i$. Explain how you will use these numbers as test materials, then demonstrate your results in the plot below.

\textbf{Explanation:}
\vspace{\stretch{1}}

\textbf{Results:}
\begin{center}
\begin{tikzpicture}
\begin{axis}[
xlabel={$Re$},
ylabel={$Im$},
axis lines=middle,
ymin=-3.5, ymax=3.5,
xmin=-3.5, xmax=3.5,
yticklabel={$\pgfmathprintnumber{\tick}i$},
width=7in,
height=7in,
grid = both,
xtick distance = 1,
ytick distance = 1,
minor y tick num = 4,
minor x tick num = 4,
grid style={draw=gray!80, dashed}
]
\end{axis}
\end{tikzpicture}
\end{center}
\item (\textbf{Argue}) Based on the model you found, explain what multiplying $w^3$ to a complex number $z$ does to $z$, and how you know it.
\vspace{\stretch{1}}
\end{enumerate}
\clearpage
}


\begin{luacode*}
utils = require("../utils")
function toFix(num, n)
	return string.format("%." .. n .. "f", num)
end
\end{luacode*}
\begin{document}
\begin{luacode*}
for i=1, 1 do
	if i == 2 then
		tex.print("\\renewcommand{\\assessmentType}{Summative}")
	end
	tex.print("\\template")
end
\end{luacode*}
\end{document}