\documentclass[twoside, 10pt]{article}
\usepackage{geometry}
\geometry{bottom=4em,top=6em, inner=2.2cm, outer=4em,  headheight=\paperheight}
\usepackage[export]{adjustbox}
\usepackage{array}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{fancyhdr}
\usepackage{luacode}
\pagestyle{fancy}
\fancyhf{}
\lhead{Alagebra II - BASE}
\chead{Polynomial III}
\directlua{pageNum = 1}
\rhead{AO Test, Page \directlua{tex.print(pageNum); pageNum = pageNum + 1; if pageNum > 3 then pageNum = 1 end}}
\usepackage{lastpage}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{pifont}
\usepackage{graphicx}
\graphicspath{{../img}}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\usepackage{tabularx}
\usepackage{polynom}

\newcommand{\R}{\mathbb R}
\newcommand{\e}{{\rm e}}
\newcommand{\pobr}[1]{\left\langle#1\right\rangle}
\newcommand{\norm}[1]{\lVert #1 \rVert}
\newcommand{\abs}[1]{\lvert #1 \rvert}

\DeclareMathOperator{\xd}{d\!}
\DeclareMathOperator{\proj}{proj}

\title{}
\date{}

\newcommand{\template}{
\directlua{tex.print(utils.genVersion())}
\noindent
{\large
First Name \rule{8em}{.4pt}\hspace{\stretch{1}} Last Name \rule{8em}{.4pt}\hspace{\stretch{1}} Date \rule{1.5em}{.4pt} -- \rule{1.5em}{.4pt} -- \rule{1.5em}{.4pt}\hspace{\stretch{1}} Period \rule{2em}{.4pt}\hspace{\stretch{1}}
}
\vspace{1em}

\noindent
\renewcommand{\arraystretch}{2}
\begin{tabular}{|l|l|l|}
\hline
\textbf{Be Precise}&\textbf{Argue}&\textbf{Model}\\
\hline
&&\\
\hline
\end{tabular}

\begin{enumerate}
\section*{\normalsize Be Precise.}
\item  The Remainder Theorem: The remainder of $p(x)$ divided by $(x-a)$ is \rule{4em}{0.4pt}.
\item A \textbf{rational function} is a quotient of two \rule{10em}{0.4pt}.
\item A \textbf{rational number} is a quotient of two  \rule{10em}{0.4pt}.
\item Given $a>0$,  express $\displaystyle \frac{\sqrt[3]{a}\cdot\sqrt[5]{a^2}}{\sqrt{a}}$ as a single power of $a$ .  \rule{10em}{0.4pt}.
\item The standard form of $(-\directlua{tex.print(utils.genRandom(2, 3))}x^{\directlua{tex.print(utils.genRandom(2,10))}})^3$ is \rule{4em}{0.4pt}, the degree is \rule{4em}{0.4pt}, the leading coefficient is \rule{4em}{0.4pt} and the constant value is \rule{4em}{0.4pt}. 
\item Write a polynomial given the following conditions:
\begin{itemize}
\item
the degree of the expression is \directlua{tex.print(utils.genRandom(3, 8))}
\item 
the leading coefficient is \directlua{tex.print(utils.genRandom(-99, 99, false, false, true))}
\item the constant term is \directlua{tex.print(utils.genRandom(-99, 99, false, false, false))}
\end{itemize}
\rule{20em}{.4pt}
\item Find the zeros for each of the following polynomials:
\begin{enumerate}[itemsep=2em]
\item
$(x\directlua{tex.print(a1)})(x\directlua{tex.print(a2)})$\hspace{2em} \rule{15em}{.4pt}
\item
$x(x\directlua{tex.print(b1)})(x\directlua{tex.print(b2)})(x\directlua{tex.print(b3)})$ \hspace{2em} \rule{15em}{.4pt}
\item 
$(x\directlua{tex.print(c1)})^3(x\directlua{tex.print(c2)})^2$ \hspace{2em} \rule{15em}{.4pt}
\item 
$(\directlua{tex.print(d1)}x\directlua{tex.print(d3)}) (\directlua{tex.print(d2)}x \directlua{tex.print(d4)})$ \hspace{2em} \rule{15em}{.4pt}
\end{enumerate}
\item 
Choose one problem to solve:
\begin{enumerate}
\item
(\textbf{Rebuild})
The expression $x^2  + 11x - 80$ is equivalent to 

A. $(x-8)(x+10)$\hfill B. $(x-2)(x+40)$ \hfill C. $(x+2)(x-40)$ \hfill D. $(x+16)(x-5)$ 
\item
(\textbf{Recap})  Factor the polynomial $x^2 +14x -120$.
\vspace{\stretch{1}}
\end{enumerate}
\section*{\normalsize Argue. }
\item Choose one set of problems (either \textbf{Recap} or \textbf{Rebuild}) to solve. \textbf{Circle the label of the problem set.}

{\bf Rebuild:}
\begin{enumerate}
\item Use the quadratic formula to solve $2x^2 - 4x - \directlua{tex.print(utils.genRandom(1,9))} = 0$, and express the answer in simplest
radical form. 
\item Find the remainder of $x^2 - x - 6$ divided by $x\directlua{tex.print(utils.genRandom(-9, 9, true, false, true))}$. Show all your work!
\item \directlua{a = utils.genRandom(-5,5, true, true, true)} Factor the binomial $x^2\directlua{tex.print(a)}x$ completely. Show all your work!
\end{enumerate}

\textbf{Recap:}
\begin{enumerate}
\item Finish the proof of the remainder theorem.

{\bf Proof:} Suppose $p(x) = q(x)(x-a) + r$, then 
\begin{align*}
p(a) & = q(\rule{2em}{0.4pt})(\rule{2em}{0.4pt} - a) + r\\
& = q(\rule{2em}{0.4pt})(\rule{2em}{0.4pt}) + r\\
&=\rule{2em}{0.4pt}
\end{align*}

\item Use the remainder theorem to determine if $x\directlua{tex.print(utils.genRandom(-3, 3, true, false, true))}$ is a factor of $x^3 - x^2 - x + 1$. Show all your work!
\item \directlua{a = utils.genRandom(-5,5); b = utils.genRandom(-5,5, false, false, -a);c = utils.genRandom(-5,5)} Factor the polynomial $(x\directlua{tex.print(utils.normalizeCoeff(c, true))})^2\directlua{tex.print(utils.normalizeCoeff(a+b, true))}(x\directlua{tex.print(utils.normalizeCoeff(c, true))})\directlua{tex.print(utils.normalizeCoeff(a*b, true))}$ completely. Show all your work!
\end{enumerate}
\item Determine the product of $(\directlua{tex.print(d1)}x\directlua{tex.print(a1)})$ and $(-4x^2 + x - 2)$. Express the product in standard form. {\bf Show all your work!}
\vspace{\stretch{1}}
\clearpage
\item Find the result when $\directlua{tex.print(d2)}x^2 \directlua{tex.print(a2)}x + 4$ is subtracted from $x^2 + 2x \directlua{tex.print(d4)}$. {\bf Show all your work!}
\vspace{\stretch{1}}
\item 
Choose one problem to solve. Circle the label of the problem that you choose.
\begin{enumerate}
\item
(\textbf{Rebuild}) Let $f(x) = (x\directlua{tex.print(utils.genRandom(-5,5, true, false, true))})(x\directlua{tex.print(utils.genRandom(-5,5, true, false, true))})(x\directlua{tex.print(utils.genRandom(-5,5, true, false, true))})$. Find all intercepts of $f(x)$ (including both horizontal and vertical). {\bf Show your reasoning!}
\item
(\textbf{Recap}) 
Let $f(x) = (x - 10)(x + 3)$. {\bf Explain} how you will choose the smallest graphing window in the form of ``$-a \leq x\leq a$, $-b \leq y \leq b$'' such that it contains all intercepts (both horizontal and vertical).
\vspace{\stretch{1}}
\end{enumerate}
\section*{\normalsize Model. }
\item Choose one set of problems (either \textbf{Recap} or \textbf{Rebuild}) to solve. \textbf{Circle the label of the problem set.}
{\bf Rebuild:}
\begin{enumerate}
\item 
\directlua{x = utils.genRandom(2, 10); y = x + utils.genRandom(1,5); total = 0.25*x + 0.1*y;}
Josie has \$\directlua{tex.print(total)} in dimes and quarters. She has \directlua{tex.print(y-x)} more dimes than quarters. Establish an equation that can be used to determine $x$, the number of quarters she has.
\item Vince wants to rent a canoe while he is on vacation. The canoe rental company charges \$18 for the first hour and \$\directlua{price=toFix(utils.genRandom(10,20)/2, 2); tex.print(price)} for each additional hour, x. If Vince has \$78 to spend on renting a canoe, write an inequality in terms of $x$ that models this situation.
\end{enumerate}
{\bf Recap:}
\begin{enumerate}
\item \directlua{num=utils.genRandom(1, 9); den=utils.genRandom(num, 20)} Find the number that is $\displaystyle \frac{\directlua{tex.print(num)}}{\directlua{tex.print(den)}}$ less than its reciprocal.
\end{enumerate}
\vspace{\stretch{1}}
\end{enumerate}
\clearpage
}


\begin{luacode*}
utils = require("../utils")
a1 = utils.genRandom(-5,5, true, false, true)
a2 = utils.genRandom(a1+1,a1+5, true, false, true)
b1 = utils.genRandom(-10,10, true, false, true)
b2 = utils.genRandom(b1+1,b1+5, true, false, true)
b3 = utils.genRandom(b2+1,b2+5, true, false, true)
c1 = utils.genRandom(-10,10, true, false, true)
c2 = utils.genRandom(c1+1,c1+5, true, false, true)
d1 = utils.genRandom(2,10, false, false, true)
d2 = utils.genRandom(d1+1,11, false, false, true)
d3 = utils.genRandom(-10,10, true, false, true)
d4 =  utils.genRandom(-10,10, true, false, true)
function toFix(num, n)
	return string.format("%." .. n .. "f", num)
end
\end{luacode*}
\begin{document}
\begin{luacode*}
for i=1,3 do
	tex.print("\\template")
end
\end{luacode*}
\end{document}