\documentclass[twoside, 10pt]{article}
\usepackage{geometry}
\geometry{bottom=4em,top=6em, inner=2.2cm, outer=4em,  headheight=\paperheight}
\usepackage[export]{adjustbox}
\usepackage{array}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{fancyhdr}
\usepackage{luacode}
\pagestyle{fancy}
\fancyhf{}
\lhead{Alagebra II - BASE}
\chead{Polynomial I}
\directlua{pageNum = 1}
\rhead{AO Test, Page \directlua{tex.print(pageNum); pageNum = pageNum + 1; if pageNum > 2 then pageNum = 1 end}}
\usepackage{lastpage}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{pifont}
\usepackage{graphicx}
\graphicspath{{../img}}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\usepackage{tabularx}
\usepackage{polynom}

\newcommand{\R}{\mathbb R}
\newcommand{\e}{{\rm e}}
\newcommand{\pobr}[1]{\left\langle#1\right\rangle}
\newcommand{\norm}[1]{\lVert #1 \rVert}
\newcommand{\abs}[1]{\lvert #1 \rvert}

\DeclareMathOperator{\xd}{d\!}
\DeclareMathOperator{\proj}{proj}

\title{}
\date{}

\newcommand{\template}{
\directlua{tex.print(utils.genVersion())}
\noindent
{\large
First Name \rule{6em}{.1pt}\hspace{\stretch{1}} Last Name \rule{6em}{.1pt}\hspace{\stretch{1}} Date \rule{1.5em}{.1pt} -- \rule{1.5em}{.1pt} -- \rule{1.5em}{.1pt}\hspace{\stretch{1}} Period \rule{2em}{.1pt}\hspace{\stretch{1}} Score \rule{2em}{.1pt}
}
\vspace{1em}

\noindent\textbf{Instruction: No calculator in this action opportunity. In particular, you are required to simplify all additions and subtractions.}
\begin{enumerate}
\item ({\textbf{Be Precise}}) Score: \rule{2em}{.4pt} 
\begin{enumerate}
\item
Identify the degree, leading coefficient, and constant value of the
following polynomial:
\vspace{1em}

 $\directlua{tex.print(utils.genRandom(-10,10, false, true, true))} x^{\directlua{tex.print(utils.genRandom(1,10,false, true,true))}}\directlua{tex.print(utils.genRandom(-10,10, true, true, true))} x^{\directlua{tex.print(utils.genRandom(11,20,false, true,true))}}\directlua{tex.print(utils.genRandom(-10,10, true, true, true))} x^{\directlua{tex.print(utils.genRandom(1,10,false, true,true))}}\directlua{tex.print(utils.genRandom(-200,200, true, false, true))} $. Degree: \rule{3em}{0.4pt} Leading Coefficient: \rule{3em}{0.4pt} Constant Value: \rule{3em}{0.4pt}

 \item Write the expression in standard form:
$
 (\directlua{tex.print(utils.genRandom(-10,10, false, true, true))} x \directlua{tex.print(utils.genRandom(-10,10, true, true, true))} x^3\directlua{tex.print(utils.genRandom(-10,10, true, true, true))}x^2 ) - (\directlua{tex.print(utils.genRandom(-10,10, false, true, true))}x^2  \directlua{tex.print(utils.genRandom(-10,10, true, true, true))} x \directlua{tex.print(utils.genRandom(-10,10, true, true, true))} )
$
\vspace{1em}

\rule{20em}{0.4pt}
\item
$\log_c(c^{\directlua{tex.print(utils.genRandom(-10,10, false, true, true))} x^2 \directlua{tex.print(utils.genRandom(-10,10, true, true, true))} x}) = $ \rule{3em}{0.4pt}
\item $\sqrt[\directlua{n =utils.genRandom(1,10, false, true, 2); tex.print(n)}]{x^{\directlua{m =utils.genRandom(1,10, false, true, n); tex.print(m)}}} = x^{(\rule{2em}{0.4pt})}$
\item In the discrete exponential growth model $2026(\directlua{tex.print(utils.genRandom(1,99)/1000+1)})^t$, the growth factor is \rule{3em}{0.4pt}, and the growth rate is \rule{3em}{0.4pt} \%.
\item In the continuous exponential growth model $2025e^{\directlua{tex.print(utils.genRandom(1,99)/1000)}t}$, the growth factor is \rule{3em}{0.4pt}, and the growth rate is \rule{3em}{0.4pt}\%.
\end{enumerate}

\item ({\textbf{Argue}}) Score: \rule{2em}{.4pt} 
\begin{enumerate}
\item
Given $f(x) = \directlua{tex.print(utils.genRandom(-10,10, false, true, true))}x \directlua{tex.print(utils.genRandom(-10,10, true, false, true))}$, write the equation of $f^{-1}(x)$. \textbf{Show your work.}
\vspace{\stretch{1}}
\item  What is the solution to $ \directlua{tex.print(utils.genRandom(2,10))}\left( \directlua{tex.print(utils.genRandom(2,10))}\right)^{ \directlua{tex.print(utils.genRandom(-10,10, false, true, true))}x} =  \directlua{tex.print(utils.genRandom(1,20))}$? \textbf{Show your work, and express your answer in exact form through mathematics notation. No decimal.}
\vspace{\stretch{1}}
\end{enumerate}
\clearpage
\item ({\textbf{Model}}) Score: \rule{2em}{.4pt} 

\textbf{Choose one problem to solve:}
\begin{enumerate}
\item(\textbf{Rebuild}) Suppose the sum of two numbers is $\directlua{tex.print(utils.genRandom(-100, 100))}$. Denote one of the numbers by $x$.
\begin{enumerate}
\item Write an expression for the product of these two numbers, $P(x)$. \textbf{Show your reasoning.}
\vspace{\stretch{1}}
\item What is the product of the two numbers when $x=\directlua{tex.print(utils.genRandom(-50, 50))}$. \textbf{Show your reasoning.}
\vspace{\stretch{1}}
\item What is the reasonable domain of $P(x)$? \textbf{Show your reasoning.}
\vspace{\stretch{1}}
\end{enumerate}

\item (\textbf{Recap})
Mai wants to make an open-top box by cutting out the corners of a square piece of cardboard and folding up the sides. The cardboard is \directlua{a = utils.genRandom(10,20, false, false,false); tex.print(a)} centimeters by \directlua{tex.print(a)} centimeters. The volume $V(x)$ in cubic centimeters of the open-top box is a function of the side length $x$,
in centimeters, of the square cutouts.
\begin{enumerate}
\item Write an expression for $V(x)$. \textbf{Show your reasoning.}
\vspace{\stretch{1}}
\item What is the volume of the box when $x=\directlua{tex.print(utils.genRandom(1, math.floor(a/2) - 1))}$. \textbf{Show your reasoning.}
\vspace{\stretch{1}}
\item What is the reasonable domain of $V(x)$? \textbf{Show your reasoning.}
\vspace{\stretch{1}}
\end{enumerate}
\clearpage
\end{enumerate}
\end{enumerate}
}

\begin{luacode*}
utils = require("../utils")
\end{luacode*}

\begin{document}
\begin{luacode}
for i=1,7 do
	tex.print("\\template")
end
\end{luacode}
\end{document}