\documentclass[twoside, 10pt]{article}
\usepackage{geometry}
\geometry{bottom=4em,top=6em, inner=2.2cm, outer=4em,  headheight=\paperheight}
\usepackage[export]{adjustbox}
\usepackage{array}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{fancyhdr}
\usepackage{luacode}
\newcommand{\assessmentType}{Formative}
\pagestyle{fancy}
\fancyhf{}
\lhead{Alagebra II - BASE}
\chead{Polynomial Rebuild}
\directlua{pageNum = 1}
\rhead{AO \assessmentType, Page \directlua{tex.print(pageNum); pageNum = pageNum + 1; if pageNum > 2 then pageNum = 1 end}}
\usepackage{lastpage}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{pifont}
\usepackage{graphicx}
\graphicspath{{../img}}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\usepackage{tabularx}
\usepackage{polynom}

\newcommand{\R}{\mathbb R}
\newcommand{\e}{{\rm e}}
\newcommand{\pobr}[1]{\left\langle#1\right\rangle}
\newcommand{\norm}[1]{\lVert #1 \rVert}
\newcommand{\abs}[1]{\lvert #1 \rvert}

\DeclareMathOperator{\xd}{d\!}
\DeclareMathOperator{\proj}{proj}

\title{}
\date{}

\newcommand{\template}{
\directlua{tex.print(utils.genVersion())}
\noindent
{\large
First Name \rule{8em}{.4pt}\hspace{\stretch{1}} Last Name \rule{8em}{.4pt}\hspace{\stretch{1}} Date \rule{1.5em}{.4pt} -- \rule{1.5em}{.4pt} -- \rule{1.5em}{.4pt}\hspace{\stretch{1}} Period \rule{2em}{.4pt}\hspace{\stretch{1}}
}
\vspace{1em}

\noindent
\renewcommand{\arraystretch}{2}
\begin{tabular}{|l|l|l|}
\hline
\textbf{ARGUE}&\textbf{MODEL}&\textbf{BE PRECISE}\\
\hline
&&\\
\hline
\end{tabular}

\begin{enumerate}
\section*{\normalsize Be Precise.}
 \item Write the expression in standard form:
$
 (\directlua{tex.print(utils.genRandom(-10,10, false, true, true))} x \directlua{tex.print(utils.genRandom(-10,10, true, true, true))} x^3\directlua{tex.print(utils.genRandom(-10,10, true, true, true))}x^2 ) - (\directlua{tex.print(utils.genRandom(-10,10, false, true, true))}x^2  \directlua{tex.print(utils.genRandom(-10,10, true, true, true))} x \directlua{tex.print(utils.genRandom(-10,10, true, false, true))} )
$
\vspace{2em}

\rule{20em}{0.4pt}
 \item Write the expression in standard form: $(x \directlua{tex.print(utils.genRandom(-10,10, true, false, true))})(x \directlua{tex.print(utils.genRandom(-10,10, true, false, true))})$
 \vspace{2em}

\rule{20em}{0.4pt}
 \item Write a polynomial given the following conditions:
\begin{itemize}
\item
the degree of the expression is \directlua{tex.print(utils.genRandom(3, 8))}
\item 
the leading coefficient is \directlua{tex.print(utils.genRandom(-99, 99, false, false, true))}
\item the constant term is \directlua{tex.print(utils.genRandom(-99, 99, false, false, false))}
\item it has exactly three terms
\end{itemize}
\vspace{2em}

\rule{20em}{0.4pt}
\section*{\normalsize Model. }
\item Suppose the sum of two numbers is $\directlua{tex.print(utils.genRandom(-100, 100))}$. Denote one of the numbers by $x$.
\begin{enumerate}
\item Write an expression for the product of these two numbers, $P(x)$. \textbf{Show your reasoning.}
\vspace{\stretch{1}}
\item What is the product of the two numbers when $x=\directlua{tex.print(utils.genRandom(-50, 50))}$. \textbf{Show your reasoning.}
\vspace{\stretch{1}}
\item What is the reasonable domain of $P(x)$? \textbf{Show your reasoning.}
\vspace{\stretch{1}}
\end{enumerate}
\clearpage
\section*{\normalsize Argue. }
\item \directlua{a = utils.genRandom(-5,5); b = utils.genRandom(-5,5, false, false, -a);} Solve $x^2\directlua{tex.print(utils.normalizeCoeff(a+b, true))}x\directlua{tex.print(utils.normalizeCoeff(a*b, true))} =0$ for $x$. Show all your work!
\begin{enumerate}[label = \textbf{Step \arabic*:}, leftmargin=*]
\item
Find two numbers $u$ and $v$ such that $u\cdot v = \directlua{tex.print(utils.normalizeCoeff(a*b, false))}$ and $u + v =  \directlua{tex.print(utils.normalizeCoeff(a+b, false))}$
\vspace{\stretch{1}}
\item Use the result in Step 1 to factor the polynomial of the left.
\vspace{\stretch{1}}
\item Use the factorization in Step 2 to determine the solutions of the equations.
\vspace{\stretch{1}}
\end{enumerate}
\item  Solve $ \directlua{tex.print(utils.genRandom(2,10))}\left( \directlua{tex.print(utils.genRandom(2,10))}\right)^{ \directlua{tex.print(utils.genRandom(-10,10, false, true, true))}x} =  \directlua{tex.print(utils.genRandom(1,20))}$ for $x$. \textbf{Show your work, and express your answer in exact form through mathematics notation. No decimal.}
\begin{enumerate}[label = \textbf{Step \arabic*:}, leftmargin=*]
\item
Isolate the exponential function of $x$ on one side of the equation.
\vspace{\stretch{1}}
\item Apply a logarithm of an appropriate base on both sides of the equation.
\vspace{\stretch{1}}
\item Solve the resulted linear equation from the last step.
\vspace{\stretch{1}}
\end{enumerate}
\end{enumerate}
\clearpage
}


\begin{luacode*}
utils = require("../utils")
function toFix(num, n)
	return string.format("%." .. n .. "f", num)
end
\end{luacode*}
\begin{document}
\begin{luacode*}
for i=1, 2 do
	if i == 2 then
		tex.print("\\renewcommand{\\assessmentType}{Summative}")
	end
	tex.print("\\template")
end
\end{luacode*}
\end{document}