\documentclass[twoside, 10pt]{article}

\usepackage{geometry}
\geometry{outer=3em, inner=2.2cm, top=6em, bottom=4em, headheight=\paperheight}
\usepackage[export]{adjustbox}
\usepackage{array}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\lhead{Algebra II - BASE}
\chead{Domain and Range}
\rhead{Practice, Page \thepage}
\usepackage{lastpage}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{pifont}
\usepackage{graphicx}
\graphicspath{{../img}}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\usepackage{tabularx}
\usepackage{tikz}
\usetikzlibrary{patterns}

\newcommand{\R}{\mathbb R}
\newcommand{\e}{{\rm e}}
\newcommand{\pobr}[1]{\left\langle#1\right\rangle}
\newcommand{\norm}[1]{\lVert #1 \rVert}
\newcommand{\abs}[1]{\lvert #1 \rvert}

\DeclareMathOperator{\xd}{d\!}
\DeclareMathOperator{\proj}{proj}

\title{}
\date{}

\begin{document}
\noindent
{\large
First Name \rule{6em}{.1pt}\hspace{\stretch{1}}Last Name \rule{6em}{.1pt}\hspace{\stretch{1}} Date \rule{1.5em}{.1pt} -- \rule{1.5em}{.1pt} -- \rule{1.5em}{.1pt}\hspace{\stretch{1}} Period \rule{2em}{.1pt}\hspace{\stretch{1}} Score \rule{2em}{.1pt}
}
\vspace{1em}

{\noindent \bf Learning Objectives.}
\begin{itemize}
\item State the definition of the domain and the range of a function
\item Find the domain and the range of a given function
\end{itemize}
{\noindent\bf Do Now.} {\it Work on the following problems when the teacher is taking attendance and returning works.}
\begin{enumerate}
\item In the following surveys, what are the set of input data?
\begin{enumerate}
\item
The height of all human beings on the Earth.
\vspace{\stretch{1}}
\item The height of all Americans.
\vspace{\stretch{1}}
\item The height of all Americans below age 10.
\vspace{\stretch{1}}
\end{enumerate}
\item Suppose $x$ is the width of a rectangle with length 5. The area of the rectangle can be expressed as $5x$.
\begin{enumerate}
\item
As an algebraic expression, what $x$-values are allowed to plug into $5x$? What are the possible outputs?
\vspace{\stretch{1}}
\item 
However, in the view of a rectangle, what $x$-values are allowed to plug into $5x$? What are the possible outputs?
\vspace{\stretch{1}}
\end{enumerate}
\item Does each of the following relations form a one-to-one correspondence? Explain why if it doesn't, then propose a revision that forms a  one-to-one correspondence.
\begin{enumerate}
\item student v.s. student ID number
\vspace{\stretch{1}}
\item biological son v.s. biological father
\vspace{\stretch{1}}
\end{enumerate}

\end{enumerate}

\end{document}