\documentclass[twoside, 10pt]{article}
\usepackage{geometry}
\geometry{bottom=4em,top=6em, inner=2.2cm, outer=4em,  headheight=\paperheight}
\usepackage[export]{adjustbox}
\usepackage{array}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{fancyhdr}
\usepackage{luacode}
\pagestyle{fancy}
\fancyhf{}
\lhead{Algebra II - BASE}
\chead{Radical Equations}
\directlua{pageNum = 1}
\rhead{Practice, Page \directlua{tex.print(pageNum); pageNum = pageNum + 1; if pageNum > 100 then pageNum = 1 end}}
\usepackage{lastpage}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{pifont}
\usepackage{graphicx}
\graphicspath{{../img}}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\usepackage{tabularx}
\usepackage{polynom}

\newcommand{\R}{\mathbb R}
\newcommand{\e}{{\rm e}}
\newcommand{\pobr}[1]{\left\langle#1\right\rangle}
\newcommand{\norm}[1]{\lVert #1 \rVert}
\newcommand{\abs}[1]{\lvert #1 \rvert}

\DeclareMathOperator{\xd}{d\!}
\DeclareMathOperator{\proj}{proj}

\title{}
\date{}

\newcommand{\template}{
\directlua{tex.print(utils.genVersion())}
\noindent
{\large
First Name \rule{6em}{.1pt}\hspace{\stretch{1}} Last Name \rule{6em}{.1pt}\hspace{\stretch{1}} Date \rule{1.5em}{.1pt} -- \rule{1.5em}{.1pt} -- \rule{1.5em}{.1pt}\hspace{\stretch{1}} Period \rule{2em}{.1pt}\hspace{\stretch{1}} Score \rule{2em}{.1pt}
}
\vspace{1em}
}

\begin{luacode*}
utils = require("../utils")
\end{luacode*}

\begin{document}
\template

\noindent\textbf{Learning Target: Argue.}
\begin{itemize}
\item
I can solve a radical equation.
\end{itemize}

\noindent
{\bf Practice.} Solve algebraically for all values of $m$:
\[
m - 2\sqrt{4m-3} = 3
\]
(Reference: 012636AII)
\begin{enumerate}[label = Step \arabic*.,  leftmargin=*]
\item
Separate the radical operation from the rest of the equation on one side.
\vspace{\stretch{1}}

\item
Raise both sides of the equation to the second power.
\vspace{\stretch{1}}

\item 
Turn the resulted quadratic equation to the standard form, then solve.
\vspace{\stretch{1}}

\item
Check for extraneous solutions.
\vspace{\stretch{1}}
\end{enumerate}
\clearpage

\noindent
{\bf Exit Ticket (Argue).} \hspace{2em}   Name  \rule{10em}{0.4pt}\hspace{2em}  Score \rule{2em}{0.4pt} 

Solve algebraically for all values of $x$.
\[
\sqrt{x+5} - x = 3
\]
(Reference: 082530AII)\begin{enumerate}[label = Step \arabic*.,  leftmargin=*]
\item
Separate the radical operation from the rest of the equation on one side.
\vspace{\stretch{1}}

\item
Raise both sides of the equation to the second power.
\vspace{\stretch{1}}

\item 
Turn the resulted quadratic equation to the standard form, then solve.
\vspace{\stretch{1}}

\item
Check for extraneous solutions.
\vspace{\stretch{1}}
\end{enumerate}

\end{document}